Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-07-27 threshold/draft.Rnw
Minor update

Finding highly-correlated pairs among a large set of vectors is an important
part of many applications. For instance, subsets of highly-correlated vectors
of gene expression values may be used in the discovery of networks of genes
relevant to particular biological processes\cite{genomics}.
Identification of highly-correlated pairs may be used in feature selection
algorithms for machine learning applications\cite{ml1, ml2}. It's also
important to many time series and image processing applications, see for
example\cite{timeseries, svd-similarity} and references therein.

>>>>

Finding highly-correlated pairs among a large set of vectors is an important
part of many applications. For instance, subsets of highly-correlated vectors
of gene expression values may be used in the discovery of networks of genes
relevant to particular biological processes\cite{genomics}.  Identification of
highly-correlated pairs may be used in feature selection algorithms for machine
learning applications\cite{ml1, ml2} and are also important to time series
and image processing applications\cite{timeseries, svd-similarity}.
